### 2009-03-23 doc/storage_system/arc-storage-documentation.tex
some updates

%%%%---- The title ----
{\centering \textsc{\Large Documentation of the ARC storage system}\Large \par}
\vspace*{0.5cm}

%%%%---- A subtitle, if necessary ----
{\centering \textit{\large First prototype status and plans}\large \par}

@@

    \item[ReplicatedAHash] %TODO: describe ReplicatedAHash, sendMessage, processMessage
	is a subclass of the \verb!CentralizedAHash! business logic class and implements the extra logic needed for communication between A-Hash instances. The \verb!ReplicatedAHash! adds the method \verb!sendMessage! to the A-Hash interface and has a method \verb!processMessage! for processing messages from \verb!sendMessage!. These two methods are needed for the communication framework of the \verb!ReplicationManager!. The actual replication is managed by the \verb!ReplicationStore! and \verb!ReplicationManager!, meaning that the \verb!ReplicatedAHash!, with the exception of the above mentioned methods, is actually just a centralized A-Hash with a specific storage module.
    \item[ReplicationStore] %TODO: describe ReplicationStore, connection with TransDBStore, config, etc.
	is a specialized replicated DB. It is a subclass of \verb!TransDBStore!\footnote{A module for storing data on disk transactionally using the Berkeley DB library.} with some additional features for handling replication. The \verb!ReplicationStore! periodically updates an A-Hash object containing information about the current master A-Hash and available clients. In addition it contains a \verb!ReplicationManager! object which governs the replication framework.
    \item[ReplicationManager] %TODO: describe ReplicationManager, elections, communication (interservice communication, security, callback functions)
	handles all aspects of the Berkeley DB API and takes care of replicas, elections and replication messages.
	\begin{itemize}
	\item The replicated A-Hash consists of a set of replicas; one master and multiple clients. This means that the entire database is fully replicated on all replicas. When the master receives a write message, it will broadcast this message to all clients. To make sure that the db is consistent and that there will always be possible to elect a master, the master requires an acknowledgement message from a quorum of clients before continuing.
	\item In the replicated A-Hash there is one master and multiple clients. When the A-Hash starts up or if a master goes offline, we need to find a new master. This is solved by the clients holding an election, according to the Paxos algorithm. Simply told, all clients sends a vote to all other clients, and the eligible client that gets the most votes wins the election. An eligible client is a client which has received the latest updates. (See the Berkeley DB documentation for more details.) There are cases where some servers are more suitable to be master than others (better hardware, faster Ethernet, etc.). In such cases you can influence the election by setting a higher priority on the best servers. While an election is being held, it is not possible to write or read from the A-Hash, as consistency cannot be guaranteed without a master.
	\item As the replicas in the replicated A-Hash are services running within HED, the replication messages needs to be sent through the communication framework of HED. To be able to use this framework, the Berkeley DB needs a callback function for sending messages and the \verb!ReplicationManager! needs to call Berkeley DB to process incoming messages. The \verb!ReplicationMessage! takes a send function as one of the initialization arguments, and calls this function in the callback method. By providing the \verb!ReplicatedAHash.sendMessage! to the \verb!ReplicationManager! messages will be sent through the HED communication services just as in regular inter service communication. When \verb!ReplicatedAHash! receives a replication message from \verb!sendMessage! it will call \verb!ReplicationManager.processMessage! which in turn will call the Berkeley DB processMessage. This communication framework is both used by Berkeley DB and directly by the \verb!ReplicationManager! for, e.g., bootstrapping the A-Hash replicas and to communicate newly discovered clients.
\end{itemize}

@@

%TODO: here comes some sentences about how the Librarian reads from any A-Hash and finds the master A-Hash for writing.
The replicated A-Hash deployment is based on a single master, multiple clients scenario (see Section~\ref{sec:a_hash} for details). This means that the Librarian can read from any A-Hash, while it can only write to the master A-Hash. A list of A-Hashes, master and clients, is stored in an A-Hash object. The Librarian periodically gets this list to maintain its own list of A-Hash services. If the Librarian tries to write to the replicated A-Hash and the master is down, the Librarian will try to get a new list from one of the clients and retry the write request once before giving up. In case of reading from the replicated A-Hash, the Librarian will randomly loop through the list of clients until the read request is successful or until there are no more clients available.

>>>>

%%%%---- The title ----
{\centering \textsc{\Large Chelonia - Self-healing distributed storage system}\Large \par}
\vspace*{0.5cm}

%%%%---- A subtitle, if necessary ----
{\centering \textit{\large Documentation and developer's guide}\large \par}

@@

\begin{description}
    \item[ReplicatedAHash] 
	is a subclass of the \verb!CentralizedAHash! business logic class and implements the extra logic needed for communication between A-Hash instances. The \verb!ReplicatedAHash! adds the method \verb!sendMessage! to the A-Hash interface and has a method \verb!processMessage! for processing messages from \verb!sendMessage!. These two methods are needed for the communication framework of the \verb!ReplicationManager!. The actual replication is managed by the \verb!ReplicationStore! and \verb!ReplicationManager!, meaning that the \verb!ReplicatedAHash!, with the exception of the above mentioned methods, is actually just a centralized A-Hash with a specific storage module.
    \item[ReplicationStore] 
	is a specialized replicated DB. It is a subclass of \verb!TransDBStore!\footnote{A module for storing data on disk transactionally using the Berkeley DB library.} with some additional features for handling replication. The \verb!ReplicationStore! periodically updates an A-Hash object containing information about the current master A-Hash and available clients. In addition it contains a \verb!ReplicationManager! object which governs the replication framework.
    \item[ReplicationManager] 
	handles all aspects of the Berkeley DB API and takes care of replicas, elections and replication messages.
	\begin{itemize}
	\item The replicated A-Hash consists of a set of replicas; one master and multiple clients. This means that the entire database is fully replicated on all replicas. When the master receives a write message, it will broadcast this message to all clients. To make sure that the db is consistent and that there will always be possible to elect a master, the master requires an acknowledgement message from a quorum of clients before continuing.
	\item In the replicated A-Hash there is one master and multiple clients. When the A-Hash starts up or if a master goes offline, we need to find a new master. This is solved by the clients holding an election, according to the Paxos algorithm. Simply told, all clients sends a vote to all other clients, and the eligible client that gets the most votes wins the election. An eligible client is a client which has received the latest updates. (See the Berkeley DB documentation for more details.) There are cases where some servers are more suitable to be master than others (better hardware, faster Ethernet, etc.). In such cases you can influence the election by setting a higher priority on the best servers. While an election is being held, it is not possible to write or read from the A-Hash, as consistency cannot be guaranteed without a master.
	\item As the replicas in the replicated A-Hash are services running within HED, the replication messages needs to be sent through the communication framework of HED. To be able to use this framework, the Berkeley DB needs a callback function for sending messages and the \verb!ReplicationManager! needs to call Berkeley DB to process incoming messages. The \verb!ReplicationMessage! takes a send function as one of the initialization arguments, and calls this function in the callback method. By providing the \verb!ReplicatedAHash.sendMessage! to the \verb!ReplicationManager! messages will be sent through the HED communication services just as in regular inter service communication. When \verb!ReplicatedAHash! receives a replication message from \verb!sendMessage! it will call \verb!ReplicationManager.processMessage! which in turn will call the Berkeley DB processMessage. This communication framework is both used by Berkeley DB and directly by the \verb!ReplicationManager! for, e.g., bootstrapping the A-Hash replicas and to communicate newly discovered clients.
\end{itemize}
\end{description}

@@

The replicated A-Hash deployment is based on a single master, multiple clients scenario (see Section~\ref{sec:a_hash} for details). This means that the Librarian can read from any A-Hash, while it can only write to the master A-Hash. A list of A-Hashes, master and clients, is stored in an A-Hash object. The Librarian periodically gets this list to maintain its own list of A-Hash services. If the Librarian tries to write to the replicated A-Hash and the master is down, the Librarian will try to get a new list from one of the clients and retry the write request once before giving up. In case of reading from the replicated A-Hash, the Librarian will randomly loop through the list of clients until the read request is successful or until there are no more clients available.

### 2009-03-23 doc/storage_system/arc-storage-manual.tex
some updates

\begin{verbatim}
<Service name="pythonservice" id="shepherd">
    <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
    <ServiceID>https://storage:60000/Shepherd</ServiceID>
    <CheckPeriod>20</CheckPeriod>
    <MinCheckInterval>0.1</MinCheckInterval>
    <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
    <StoreCfg><DataDir>/var/spool/arc/shepherd_data</DataDir></StoreCfg>
    <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
    <BackendCfg>
        <DataDir>/var/spool/arc/shepherd_store</DataDir>
        <TransferDir>/var/spool/arc/shepherd_transfer</TransferDir>
        <TURLPrefix>http://storage:60001/hopi/</TURLPrefix>
    </BackendCfg>
    <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
    <BartenderURL>https://storage:60000/Bartender</BartenderURL>
    <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
</Service>
\end{verbatim}

@@

\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig 
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
>
    <Server>
        <Pidfile>/var/run/arched2.pid</Pidfile>
        <Logger level="ERROR">/var/log/arched2.log</Logger>
    </Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins><Name>mcctcp</Name></Plugins>
    <Plugins><Name>mcctls</Name></Plugins>
    <Plugins><Name>mcchttp</Name></Plugins>
    <Plugins><Name>mccsoap</Name></Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/> 
            <tcp:Listen>
                <tcp:Port>60006</tcp:Port>
                <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
            <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
            <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="shepherd">^/Shepherd$</next>
            <next id="byteio">^/byteio/</next>
        </Plexer>
        <Service name="pythonservice" id="shepherd">
            <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
            <ServiceID>https://storage2:60006/Shepherd</ServiceID>
            <CheckPeriod>20</CheckPeriod>
            <MinCheckInterval>0.1</MinCheckInterval>
            <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
            <StoreCfg>
                <DataDir>/var/spool/arc/shepherd_store2</DataDir>
            </StoreCfg>
            <BackendClass>storage.shepherd.byteio.ByteIOBackend</BackendClass>
            <BackendCfg>
                <DataDir>/var/spool/arc/shepherd_data2</DataDir>
                <TransferDir>/var/spool/arc/shepherd_transfer2</TransferDir>
                <TURLPrefix>https://storage2:60006/byteio/</TURLPrefix>
            </BackendCfg>
            <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
            <BartenderURL>https://storage:60000/Bartender</BartenderURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml"/>
        </Service>
        <Service name="pythonservice" id="byteio">
            <ClassName>storage.shepherd.byteio.ByteIOService</ClassName>
            <TransferDir>/var/spool/arc/shepherd_transfer2</TransferDir>
            <NotifyURL>https://storage2:60006/Shepherd</NotifyURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml"/>
        </Service>
    </Chain>
</ArcConfig>    
\end{verbatim}

@@

\begin{verbatim}
zsombor@storage:~$ cat /etc/arc/storage_service_3.xml 
<?xml version="1.0"?>
<ArcConfig 
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
>
    <Server>
        <Pidfile>/var/run/arched3.pid</Pidfile>
        <Logger level="ERROR">/var/log/arched3.log</Logger>
    </Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins><Name>mcctcp</Name></Plugins>
    <Plugins><Name>mcctls</Name></Plugins>
    <Plugins><Name>mcchttp</Name></Plugins>
    <Plugins><Name>mccsoap</Name></Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/> 
            <tcp:Listen>
		<tcp:Port>60010</tcp:Port>
		<tcp:Version>4</tcp:Version>
	    </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
            <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
            <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="shepherd">^/Shepherd$</next>
        </Plexer>
        <Service name="pythonservice" id="shepherd">
            <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
            <ServiceID>https://storage3:60010/Shepherd</ServiceID>
            <CheckPeriod>20</CheckPeriod>
            <MinCheckInterval>0.1</MinCheckInterval>
            <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
            <StoreCfg><DataDir>/var/spool/arc/shepherd_data3</DataDir></StoreCfg>
            <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
            <BackendCfg>
                <DataDir>/var/spool/arc/shepherd_store3</DataDir>
                <TransferDir>/var/spool/arc/shepherd_transfer3</TransferDir>
                <TURLPrefix>http://storage3:60011/hopi/</TURLPrefix>
            </BackendCfg>
            <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
            <BartenderURL>https://storage:60000/Bartender</BartenderURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
        </Service>
    </Chain>
    <Chain>
        <Component name="tcp.service" id="tcp2">
            <next id="http2"/> 
            <tcp:Listen>
		<tcp:Port>60011</tcp:Port>
		<tcp:Version>4</tcp:Version>
	    </tcp:Listen>
        </Component>
        <Component name="http.service" id="http2">
            <next id="plexer2">GET</next>
            <next id="plexer2">PUT</next>
        </Component>
        <Plexer name="plexer.service" id="plexer2">
            <next id="hopi">^/hopi/</next>
        </Plexer>
        <Service name="hopi" id="hopi">
            <DocumentRoot>/var/spool/arc/shepherd_transfer3</DocumentRoot>
            <SlaveMode>1</SlaveMode>
        </Service>
    </Chain>
</ArcConfig>    
\end{verbatim}

@@

Besides the \verb!arc_storage_cli! tool we can access the storage system with the use of a FUSE modul. We can install the ARC storage FUSE modul following these steps:

>>>>

\begin{verbatim}
<Service name="pythonservice" id="shepherd">
    <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
    <ServiceID>https://storage:60000/Shepherd</ServiceID>
    <CheckPeriod>20</CheckPeriod>
    <MinCheckInterval>0.1</MinCheckInterval>
    <CreatingTimeout>600</CreatingTimeout>
    <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
    <StoreCfg><DataDir>/var/spool/arc/shepherd_data</DataDir></StoreCfg>
    <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
    <BackendCfg>
        <DataDir>/var/spool/arc/shepherd_store</DataDir>
        <TransferDir>/var/spool/arc/shepherd_transfer</TransferDir>
        <TURLPrefix>http://storage:60001/hopi/</TURLPrefix>
    </BackendCfg>
    <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
    <BartenderURL>https://storage:60000/Bartender</BartenderURL>
    <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
</Service>
\end{verbatim}

@@

\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig 
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
>
    <Server>
        <Pidfile>/var/run/arched2.pid</Pidfile>
        <Logger level="ERROR">/var/log/arched2.log</Logger>
    </Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins><Name>mcctcp</Name></Plugins>
    <Plugins><Name>mcctls</Name></Plugins>
    <Plugins><Name>mcchttp</Name></Plugins>
    <Plugins><Name>mccsoap</Name></Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/> 
            <tcp:Listen>
                <tcp:Port>60006</tcp:Port>
                <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
            <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
            <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="shepherd">^/Shepherd$</next>
            <next id="byteio">^/byteio/</next>
        </Plexer>
        <Service name="pythonservice" id="shepherd">
            <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
            <ServiceID>https://storage2:60006/Shepherd</ServiceID>
            <CheckPeriod>20</CheckPeriod>
            <MinCheckInterval>0.1</MinCheckInterval>
            <CreatingTimeout>600</CreatingTimeout>
            <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
            <StoreCfg>
                <DataDir>/var/spool/arc/shepherd_data2</DataDir>
            </StoreCfg>
            <BackendClass>storage.shepherd.byteio.ByteIOBackend</BackendClass>
            <BackendCfg>
                <DataDir>/var/spool/arc/shepherd_store2</DataDir>
                <TransferDir>/var/spool/arc/shepherd_transfer2</TransferDir>
                <TURLPrefix>https://storage2:60006/byteio/</TURLPrefix>
            </BackendCfg>
            <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
            <BartenderURL>https://storage:60000/Bartender</BartenderURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml"/>
        </Service>
        <Service name="pythonservice" id="byteio">
            <ClassName>storage.shepherd.byteio.ByteIOService</ClassName>
            <TransferDir>/var/spool/arc/shepherd_transfer2</TransferDir>
            <NotifyURL>https://storage2:60006/Shepherd</NotifyURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml"/>
        </Service>
    </Chain>
</ArcConfig>    
\end{verbatim}

@@

\begin{verbatim}
zsombor@storage:~$ cat /etc/arc/storage_service_3.xml 
<?xml version="1.0"?>
<ArcConfig 
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
>
    <Server>
        <Pidfile>/var/run/arched3.pid</Pidfile>
        <Logger level="ERROR">/var/log/arched3.log</Logger>
    </Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins><Name>mcctcp</Name></Plugins>
    <Plugins><Name>mcctls</Name></Plugins>
    <Plugins><Name>mcchttp</Name></Plugins>
    <Plugins><Name>mccsoap</Name></Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/> 
            <tcp:Listen>
		<tcp:Port>60010</tcp:Port>
		<tcp:Version>4</tcp:Version>
	    </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
            <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
            <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="shepherd">^/Shepherd$</next>
        </Plexer>
        <Service name="pythonservice" id="shepherd">
            <ClassName>storage.shepherd.shepherd.ShepherdService</ClassName>
            <ServiceID>https://storage3:60010/Shepherd</ServiceID>
            <CheckPeriod>20</CheckPeriod>
            <MinCheckInterval>0.1</MinCheckInterval>
            <CreatingTimeout>600</CreatingTimeout>
            <StoreClass>arcom.store.cachedpicklestore.CachedPickleStore</StoreClass>
            <StoreCfg><DataDir>/var/spool/arc/shepherd_data3</DataDir></StoreCfg>
            <BackendClass>storage.shepherd.hardlinkingbackend.HopiBackend</BackendClass>
            <BackendCfg>
                <DataDir>/var/spool/arc/shepherd_store3</DataDir>
                <TransferDir>/var/spool/arc/shepherd_transfer3</TransferDir>
                <TURLPrefix>http://storage3:60011/hopi/</TURLPrefix>
            </BackendCfg>
            <LibrarianURL>https://storage:60000/Librarian</LibrarianURL>
            <BartenderURL>https://storage:60000/Bartender</BartenderURL>
            <ClientSSLConfig FromFile="/etc/arc/clientsslconfig.xml" />
        </Service>
    </Chain>
    <Chain>
        <Component name="tcp.service" id="tcp2">
            <next id="http2"/> 
            <tcp:Listen>
		<tcp:Port>60011</tcp:Port>
		<tcp:Version>4</tcp:Version>
	    </tcp:Listen>
        </Component>
        <Component name="http.service" id="http2">
            <next id="plexer2">GET</next>
            <next id="plexer2">PUT</next>
        </Component>
        <Plexer name="plexer.service" id="plexer2">
            <next id="hopi">^/hopi/</next>
        </Plexer>
        <Service name="hopi" id="hopi">
            <DocumentRoot>/var/spool/arc/shepherd_transfer3</DocumentRoot>
            <SlaveMode>1</SlaveMode>
        </Service>
    </Chain>
</ArcConfig>    
\end{verbatim}

@@

\section{Make the A-Hash service replicated} % (fold)
\label{sec:make_the_a_hash_service_replicated}

Now we have a deployement, where one machine has the A-Hash, Librarian and Bartender services, and all three machines have a Shepherd and a storage element service. The A-Hash service stores all the metadata of all the files and collections, so it is critical. If the first machine goes offline then the whole system dies. We can deploy the A-Hash service on all the machines and still can have one consistent metadata database. The replicated version of the A-Hash uses the Berkeley DB to provide a distributed database.

Let's install Berkeley DB as root (but you can use the \verb!--prefix! option of \verb!configure! to install it somewhere else than the default location).

Get the latest Berkeley DB and its patches:
\begin{verbatim}
$ wget http://download.oracle.com/berkeley-db/db-4.7.25.tar.gz
$ wget http://www.oracle.com/technology/products/berkeley-db/db/update/4.7.25/patch.4.7.25.1
$ wget http://www.oracle.com/technology/products/berkeley-db/db/update/4.7.25/patch.4.7.25.2
$ wget http://www.oracle.com/technology/products/berkeley-db/db/update/4.7.25/patch.4.7.25.3
\end{verbatim}

Extract it and apply the patches:
\begin{verbatim}
$ tar zxf db-4.7.25.tar.gz
$ cd db-4.7.25
$ patch -p 0 < ../patch.4.7.25.1
$ patch -p 0 < ../patch.4.7.25.2
$ patch -p 0 < ../patch.4.7.25.3
\end{verbatim}

Configure, make and install it (you can use the \verb!--prefix! option for \verb!configure!)
\begin{verbatim}
$ cd build_unix/
$ ../dist/configure
\end{verbatim}

Now compile and install it:
\begin{verbatim}
$ make
$ sudo make install
\end{verbatim}

Now we need the python wrapper for the Berkeley DB:

\begin{verbatim}
$ wget http://pypi.python.org/packages/source/b/bsddb3/bsddb3-4.7.5.tar.gz
\end{verbatim}

Let's install it to the default location:

\begin{verbatim}
$ tar zxf bsddb3-4.7.5.tar.gz
$ cd bsddb3-4.7.5
$ sudo python setup.py install
\end{verbatim}

If you've installed Berkeley DB somewhere else, or want to install the python wrapper to somewhere else than the default:

\begin{verbatim}
$ BERKELEYDB_DIR=/path/to/berkeleydb python setup.py install --prefix=/where/to/install
\end{verbatim}

Let's test the installation with the \verb!test.py! included in the directory of the python wrapper for the Berkeley DB:
\begin{verbatim}
$ sudo python test.py
[...]
Ran 383 tests in 29.858s

OK
\end{verbatim}

\section{Using the FUSE module} % (fold)
\label{sec:using_the_fuse_module}

Besides the \verb!arc_storage_cli! tool we can access the storage system with the use of a FUSE module. We can install the ARC storage FUSE module following these steps:
